SubsidyExplorer - Step 7: Pre-Populated Proposals

### 2021-10-19 scripts/05_subsidy_reform_definitions.Rmd
subs affected for Anthony

title: "SubsidyExplorer - Step 4: Apply proposal 'definitions' to vessel list"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"

>>>>

title: "SubsidyExplorer - Step 5: Apply proposal 'definitions' to vessel list"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"

### 2021-10-19 scripts/06_run_model.Rmd
running another mgmt threshold for comparison
updating static result
subs affected for Anthony

This script generates alternative global and regional results.

>>>>

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers. This is effectively the reference case scenario for our model, which will be used later as a benchmark to which we can compare the results of specific proposals.

### 2021-10-19 scripts/07_proposals.Rmd
subs affected for Anthony

title: "SubsidyExplorer - Step 6: Run Model"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

>>>>

title: "SubsidyExplorer - Step 7: Pre-Populated Proposals"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---
